\cvsection{Professional Experience}

\begin{cventries}

  \cventry
  {Principal Platform Consultant (Contract)} % Title
  {Barclays (Payments Incubator)} % Company
  {London, UK} % Location
  {Oct. 2025 - Present} % Date
  {
    \begin{cvitems}
      \item {\textbf{Greenfield IDP Engineering:} Architected and built a high-performance Internal Developer Platform (IDP) on AWS and Kubernetes (EKS).
                  Managed configuration via Helm and GitHub, developing "Golden Path" templates in Go/Python that abstract complexity
                  and optimise DevEx.}
      \item {\textbf{Embedded Workforce Transformation:} Operating as a technical "player-coach" within legacy software teams. I drive Cloud-Native adoption
                  through daily pair programming, upskilling engineers on CI/CD pipelines and SRE best practices to ensure long-term autonomy.}
      \item {\textbf{High-Stakes Execution:} Technical Authority for critical payment rails. Delivering a secure, self-service ecosystem that balances strict
                  financial governance with the agility required for high-throughput data integrations and future GenAI workloads.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  %---------------------------------------------------------
  \cventry
  {Engineering Manager, Platform Lead (Consultant)} % Title
  {JPMorgan Chase / Core Engineering Consulting Group} % Company
  {London, UK} % Location
  {Apr. 2023 - Sep. 2025} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Embedded Scaling \& Enablement:} Embedded within the Cloud Enablement team to drive technical scaling from 3 to 50+ engineers.
                  I paired daily with the workforce to establish a "You Build It, You Run It" culture, upskilling teams on SRE best practices and modern cloud-native tech.}
      \item {\textbf{Hyper-Scale Kubernetes Architecture:} Architected and engineered the firm-wide GCP foundation and Kubernetes ecosystem (100+ clusters).
                  Delivered AI-ready blueprints integrating Vertex AI and data pipelines, enabling secure transition to data-intensive GenAI workloads.}
      \item {\textbf{Golden Path Engineering:} Engineered a "Golden Path" strategy that abstracted infrastructure complexity using Crossplane and GitOps.
                  Drastically reduced cognitive load and improved DevEx and system observability (Prometheus/Grafana) for thousands of internal developers.}
      \item {\textbf{Strategic Technical Execution:} Acted as a bridge between business goals and engineering execution. Translated high-level objectives into
                  executable technical roadmaps and managed the hands-on delivery of complex distributed systems.}
    \end{cvitems}
  }

  \cventry
  {Infrastructure DevOps Lead (Contract)} % Title
  {Deloitte} % Company
  {Copenhagen, Denmark} % Location
  {Mar. 2021 - Mar. 2023} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Hands-on Embedded Leadership:} Embedded as the technical lead for Denmark's critical Property Tax Platform.
                  I actively coded alongside cross-functional engineers, breaking down architectural silos and upskilling the team to own the solution independently.}
      \item {\textbf{Infrastructure Modernisation:} Parachuted in to audit and execute a ruthlessly efficient consolidation strategy for a sprawling infrastructure estate.
                  Simplified legacy complexity and slashed monthly cloud operational costs on AWS while boosting system performance.}
      \item {\textbf{API Gateway Re-Engineering:} Eradicated high-risk technical debt by replacing brittle custom authentication with managed
                  AWS API Gateway.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Principal Consultant - Azure} % Job Title
  {Microsoft} % Company
  {London, UK} % Location
  {Nov. 2020 - Mar. 2021} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{High-Frequency Trading Acceleration:} Rescued a stalled on-prem to Azure migration for a major trading platform.
                  Optimised AKS and EventHubs architectures to handle massive throughput, condensing the delivery timeline from years to months.}
      \item {\textbf{Strategic Enablement:} Delivered the first fully automated development environment, acting as the technical bridge
                  between client business units and Microsoft Product Engineering to unblock critical delivery paths.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Lead Platform Engineer - GCP} % Job Title
  {Loveholidays} % Company
  {London, UK} % Location
  {Mar. 2020 - Oct. 2020} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Performance Engineering:} Diagnosed and resolved critical latency bottlenecks in the core search engine.
                  Profiled Go/Java microservices to optimise Kubernetes autoscaling, achieving a 30\% performance increase.}
      \item {\textbf{Event-Driven Architecture:} Designed and developed a custom Go library for real-time database synchronisation
                  via GCS, reducing data propagation latency from minutes to seconds to improve customer search accuracy.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Lead DevOps Engineer - GCP} % Job Title
  {eBay} % Company
  {Berlin, Germany} % Location
  {Jun. 2019 - Mar. 2020} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Global Cloud Transformation:} Orchestrated the strategic migration of eBay’s Classifieds vertical to Google Cloud (GCP).
                  Architected standardised GKE workflows to enable rapid deployment for distributed engineering teams across Europe.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Senior DevOps Engineer / Consultant} % Job Title
  {Previous Engagements (Select Highlights)} % Company
  {Europe} % Location
  {2010 - 2019} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Deloitte (Copenhagen):} Architected immutable AWS infrastructure for critical Danish Tax systems,
                  introducing Terraform (IaC) to reduce deployment frequency from weeks to hours.}
      \item {\textbf{Element Insurance (Berlin):} Built the greenfield AWS/Kubernetes foundation for a high-growth FinTech startup,
                  serving as Interim Team Lead to scale early engineering capability.}
      \item {\textbf{HMRC (London):} Core WebOps Engineer for the UK's hyper-scale digital tax platform;
                  contributed to open-source tooling to ensure multi-cloud resilience during peak filing windows.}
      \item {\textbf{Google (London/Dublin):} Developed Python/App Engine automation tools to optimise internal engineering workflows,
                  awarded multiple peer bonuses for code quality and innovation.}
    \end{cvitems}
  }

\end{cventries}