%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Executive Profile}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
      Forward Deployed Engineer with 15+ years of experience architecting and engineering hyper-scale distributed
      systems. I operate at the intersection of technical strategy and hands-on execution, embedding directly
      with client teams to deliver mission-critical infrastructure while simultaneously elevating their engineering
      capabilities. I specialise in translating business objectives into robust "Golden Path" Internal Developer
      Platforms, leveraging AWS/Azure/GCP to ensure delivery impact while cultivating
      team autonomy through mentorship and technical leadership.

      \begin{itemize}[nosep]
            \item \textbf{Strategic Technical Delivery:} I bridge the gap between architectural vision and production reality. I partner with
                  leadership to define technical roadmaps and then lead the hands-on implementation, delivering firm-wide infrastructure
                  (e.g., global Kubernetes fleets managed via GitHub and Helm) that directly enables business goals.
            \item \textbf{Advanced Cloud Native Engineering:} Deep expertise in orchestrating massive container ecosystems.
                  I extend Kubernetes primitives using custom controllers and Operators (Go/Python) effectively solving complex
                  multi-tenant and cross-cloud challenges.
            \item \textbf{Embedded Enablement \& Leadership:} I drive culture change by working alongside engineers. I assume a "playing coach" role—pairing,
                  mentoring, and upskilling teams on complex CI/CD pipelines and modern stacks to instil engineering rigour and ensure system evolution.
            \item \textbf{SRE \& Operational Resilience:} I engineer reliability into the core platform. I champion a Site Reliability Engineering
                  culture, implementing observability, error budgeting, and self-healing mechanisms to guarantee high availability and system resilience under scale.
      \end{itemize}
\end{cvparagraph}