%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[12pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./simon.png}
\name{}{Simon Aquino}
\position{Engineering Manager{\enskip\cdotp\enskip}Head of Platform{\enskip\cdotp\enskip}Cloud-Native Architect (GCP/AWS/Azure)}%
\address{London, United Kingdom (open to relocation)}
\mobile{+44 (0) 7514 902 489}
\email{simon.aquino@gmail.com}
%\dateofbirth{January 1st, 1970}
\homepage{www.simonaquino.com}
\github{queeno}
\linkedin{linkedin.com/in/simonaquino}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \x{x-id}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \telegram{telegram-username}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}
\extrainfo{\faFlag\acvHeaderIconSep\enskip UK \& EU Citizen}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Hiring Management Team}
  {Target Company Name\\Address Line 1\\City, Country}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for Engineering Manager / Principal Engineer}
% How the letter is opened
\letteropening{Dear Hiring Team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
{\today}
{Simon Aquino~~~·~~~Cover Letter}
{}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  \lettersection{About Me}
  I am a hands-on Engineering Leader and Cloud-Native Architect with over 15 years of experience
  building scalable, high-performance systems for global enterprises like J.P. Morgan Chase, Barclays,
  Deloitte, Ebay, and Microsoft. My career has been defined by a dual focus: technical excellence
  in distributed systems (Kubernetes, AWS/GCP, Go) and organizational leadership that scales engineering
  units from seed teams to 50+ engineers. I am a "builder-leader" who thrives at the intersection of
  complex architectural challenges and high-growth team dynamics.

  \lettersection{Why You?}
  I am drawn to organisations that view platform engineering not just as infrastructure, but as a strategic
  multiplier for product velocity. Your commitment to innovation and solving hard technical
  problems aligns perfectly with my own philosophy. I am particularly excited by the opportunity
  to apply my experience in designing "Golden Path" platforms and event-driven architectures to
  help your teams move faster, safely. Whether it is modernising legacy estates or building
  greenfield AI-ready infrastructure, I want to be part of a culture that obsessively focuses on
  Developer Experience (DevEx) and operational excellence.

  \lettersection{Why Me?}
  Throughout my career, I have consistently bridged the gap between business strategy and technical
  execution. At JPMC, I scaled a Cloud Enablement unit from 3 to 50+ engineers, architecting a
  firm-wide GCP foundation. At Barclays, I acted as the Technical Authority for a payments incubator,
  modernising critical rails on AWS. I bring deep expertise in Cloud-Native ecosystems (Kubernetes,
  Terraform, Crossplane) and a proven track record of embedding security and compliance (NIST, ISO)
  without sacrificing speed. I don't just manage teams; I code alongside them, fostering a culture of
  ownership, curiosity, and high trust. I am ready to bring this blend of strategic vision and hands-on
  capability to drive your engineering goals forward.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
