\cvsection{Professional Experience}

\begin{cventries}

  \cventry
  {Engineering Manager, Data Engineering (via Core Engineering Consulting Group)} % Title
  {Haleon} % Company
  {London, UK} % Location
  {Mar. 2026 - Present} % Date
  {
    \begin{cvitems}
      \item {\textbf{Team Building \& People Leadership:} Founded and grew a team of 6 engineers from zero, owning 
                the full employee lifecycle: hiring, onboarding, performance reviews, 1:1 coaching, and career 
                development, to build a high-performing engineering culture.}
      \item {\textbf{Greenfield Delivery \& Execution:} Led the end-to-end delivery of a greenfield enterprise data 
                platform for Identity \& Access Management (IAM) governance, replacing manual audit processes with 
                automated SOX compliance reporting (PA-02/AM-02 controls).}
      \item {\textbf{Technical Strategy \& Architecture:} Defined the technical vision and platform roadmap, 
                selecting Dagster/Python for a Medallion (Bronze/Silver/Gold) ETL pipeline on Azure (AKS, ADLS Gen2, 
                PostgreSQL), and delivering infra via Terraform Cloud, Helm, and GitHub Actions.}
      \item {\textbf{Budget Ownership \& Delivery Roadmap:} Managed the project budget and delivery scope, driving 
                an iterative release strategy to incrementally ship production-grade data pipelines aligned to audit 
                timelines and regulatory deadlines.}
      \item {\textbf{AI-Assisted Ways of Working:} Led the team's adoption of AI-assisted development and AI-driven 
                code review, raising team throughput.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Principal Platform Consultant (via Red Badger)} % Title
  {Barclays} % Company
  {London, UK} % Location
  {Oct. 2025 - Mar. 2026} % Date
  {
    \begin{cvitems}
      \item {\textbf{Platform Strategy \& Transformation:} Drove the greenfield Internal Developer Platform (IDP) 
                strategy for the Payments division, defining architecture patterns on AWS/Kubernetes to modernise DevEx 
                and critical payment processing rails for high-throughput transactions.}
      \item {\textbf{Team Enablement \& Coaching:} Led the transformation of a legacy software unit into Cloud-Native 
                Platform Engineers through hands-on pair programming, mentoring the internal Tech Lead on platform 
                strategy, team structure, and engineering best practices.}
      \item {\textbf{Technical Authority \& Governance:} Acted as Technical Authority within the platform team, establishing 
                ``Golden Path'' architecture standards and automated compliance frameworks to transition legacy systems 
                into a secure, self-service ecosystem.}
    \end{cvitems}
  }

  \cventry
  {Principal Consultant, GitHub Migration (via Core Engineering Consulting Group)}
  {Haleon}
  {London, UK}
  {Apr. 2025 - Sep. 2025}
  {
    \begin{cvitems}
      \item {\textbf{Migration Delivery:} Led the technical delivery of an enterprise GitHub migration.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Engineering Manager, Cloud Enablement (via Core Engineering Consulting Group)}
  {JPMorgan Chase} % Company
  {London, UK} % Location
  {Apr. 2023 - Mar. 2025} % Date(s)
  {
    \begin{cvitems}
    \item {\textbf{Team Leadership \& Growth:} Led and grew a Cloud Enablement engineering team to 13 engineers 
      over two years, owning hiring, onboarding, performance reviews, 1:1 coaching, and career development
      to sustain a high-trust, high-delivery culture.}
    \item {\textbf{Organisational Design:} Recognised the team had outgrown its structure and built the business case 
      to the Engineering Director to split it; the proposal was approved and the resulting teams were permanently embedded 
      in the firm's org chart.}
    \item {\textbf{Technical Authority:} As the most senior lead in the Platform team, set technical direction for the firm-wide
      GCP and Kubernetes ecosystem (100+ clusters), delivered within ISO 27001/SOC 2-aligned frameworks, and mentored peer
      tech leads across the function.}
    \item {\textbf{Golden Path \& Developer Experience:} Drove a ``Golden Path'' platform strategy with Crossplane and GitOps (ArgoCD) 
      and observability via Prometheus/Grafana, lifting reliability and DevEx across teams.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Infrastructure DevOps Lead} % Job Title
  {Deloitte}
  {Copenhagen, Denmark} % Location
  {Mar. 2021 - Mar. 2023} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Cross-Team Coordination:} Led the cloud infrastructure stream for Denmark's critical Property Tax Platform,
                  coordinating across 3 satellite teams to drive delivery autonomy and resolve cross-functional architectural blockers.}
      \item {\textbf{Strategic Cost Optimisation:} Executed a high-impact infrastructure consolidation strategy, simplifying legacy complexity
                  to reduce monthly cloud operational costs without compromising system performance.}
      \item {\textbf{Modernisation \& Security:} Eliminated high-risk technical debt by replacing brittle custom authentication
                  with managed AWS API Gateway, establishing a standardised, secure pattern for external integrations.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Previous Engineering \& Leadership Roles} % Job Title
  {Microsoft, Loveholidays, eBay, Element Insurance, HMRC, Google} % Company
  {London, Berlin, Copenhagen} % Location
  {2010 - 2021} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Microsoft (Principal Consultant):} Rescued a stalled on-prem to Azure migration
              for a major trading platform, optimising AKS/EventHubs for high-frequency throughput and condensing
              delivery from years to months.}
      \item {\textbf{Loveholidays (Lead Platform Engineer):} Resolved critical latency bottlenecks in Go/Java microservices on GKE,
              achieving 30\% performance gains through Kubernetes autoscaling optimisation.}
      \item {\textbf{eBay (Lead DevOps Engineer):} Orchestrated the migration of eBay Classifieds to GCP, architecting
              standardised GKE workflows for distributed European engineering teams.}
      \item {\textbf{Earlier Career:} Greenfield AWS/K8s platforms (Element Insurance), UK Gov digital tax at scale (HMRC), and
              Python/App Engine tooling at Google, alongside IT support that earned multiple peer bonuses.}
    \end{cvitems}
  }

\end{cventries}